---
title: "p8105_hw1_qw2282"
output: github_document
---

# Problem 1


```{r}
library(tidyverse)
df_random_samp = tibble(
   rand_samp = runif(10, min = 0, max = 5),
   logical_larger_2 = rand_samp > 2,
   rand_char = c("My", "name", "is", "Qinyao", "how", "are", "you", "nice", "weather", "today"),
   rand_factor = factor(c("january", "february", "march", "april", "may", "june", "july", "august", "semptember", "october"))
)

mean(df_random_samp$rand_samp)
mean(df_random_samp$logical_larger_2)
mean(df_random_samp$rand_char)
mean(df_random_samp$rand_factor)

```


Vectors of numerical values and logicals have means while the vectors of characters and factors do not have means. This is because the numerical values can be averaged into a numerical mean. And logicals, TRUEs and FALSEs, are also stored as integers. TRUEs are stored as 1s and FALSEs are stored as 0. So when the mean function is called, the mean can be calculated with either 0 or 1. However, characters and factors are strings that do not have a numerical mean.

```{r results = 'hide'}
as.numeric(df_random_samp$logical_larger_2)
as.numeric(df_random_samp$rand_char)
as.numeric(df_random_samp$rand_factor)
```

Only the logicals and factors can be coerced into numericals. The characters cannot be converted and 'NA' is displayed for each element and a warning message poped out. 

```{r results = 'hide'}
as.numeric(as.factor(df_random_samp$rand_char))
as.numeric(as.character(df_random_samp$rand_factor))
```

When I convert the vector of characters first into factor and then into numerics, the vector is successfully converted into numbers. However, when the vector of factors first being converted into characters and then into numerics, the coercion is unsuccessful and a warning message poped out. This is because the character cannot be coerced into numericals directly. 




#Problem 2
```{r}
df_plotting = tibble(
   x = rnorm(1000),
   y = rnorm(1000),
   vec_compare = (x + y) > 0,
   num_from_logical = as.numeric(vec_compare),
   factor_from_logical = as.factor(vec_compare)
)

```

#Description of the dataset
  This data set includes `r nrow(df_plotting)` rows and `r ncol(df_plotting)` columns. This data set includes three numerical vectors: x, y and a numerical coercion of the logical vector num_from_logical; one logical vector: vec_compare; one factor vector: factor_from_logical. The mean of x is `r mean(df_plotting$x)`. the median of x is `r median(df_plotting$x)`. The proportion of TRUE in the logical vector vec_compare is `r mean(df_plotting$vec_compare)`.
  
  
```{r}

```



